Figures

### 2018-12-14 figures/05_cafos.Rmd
make gis gpkg, use 99_utils not utils

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
source("../scripts/utils.R")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
source("../scripts/99_utils.R")
```
